Geometric variational problems

### 2020-11-08 NSF2020/Description/background.tex
working on broader impacts section to include Quaife

From a phenomenological perspective, (\ref{HAP}--\ref{SL}) 
is an appropriate model of hydrophobic attraction. Specifically,
using boundary layer analysis, it is possible 
to show that $\Phi$ converges to a surface energy in the zero-decay length limit \cite{Lee2018,Lin2015,Shibata2004}.
For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g. between hydrophobic parallel disks
separated by water \cite{Eriksson1989}. Also, we have demonstrated with simulation that the forces 
derived from HAP theory are non-additive, and even deviate significantly from 
a pairwise potential \cite{Meyer2006,Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

@@

The main analytical tool of our manuscript 
is a formula for the first variation of $\Phi$ \cite{Bandle2015,Schiffer1954,Grinfeld2010}. 
This first variation  is a symmetric, rank-two tensor called the hydrophobic stress;
\begin{equation}
  \label{stress}
\boldsymbol{\sigma}_{\text{hydro}} = \gamma \rho^{-1} u^2 I + 2\rho \gamma (\tfrac{1}{2}|\nabla u|^2I - \nabla u \nabla u^T).
\end{equation}
To obtain \eqref{stress}, we observe that the potential $\Phi$ is a function of the particle position and orientations.
This is because the particle configuration defines the shape of $\Omega$ and the boundary data $f.$ 
Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
in a critical way leads to the surface term \eqref{stress}.  
By integrating the hydrophobic stress over the surface of particle $P_i,$ we obtaining the hydrophobic force and torque on each particle 
\begin{equation}
  \label{forceandtorque}
  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n} \,dS,\quad
  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times (\boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n}) \,dS.
\end{equation}
We verified that this system is force and torque free.
To supply viscous dissipation, 
we incorporated the mobility problem in Stokes flow to obtain the rigid body motions; 
\begin{equation}
\label{eq:stokes}
\begin{aligned}
&-\mu \Delta {\bf u} + \nabla p = 0, \quad \text{in}\ \Omega, \qquad 
\nabla \cdot {\bf u} = 0,  \quad \text{in}\ \Omega,\\
&{\bf u}({\bf x}) \to 0 \quad \text{as}\ |{\bf x}|\to \infty,\qquad 
  \mathbf{u}(\mathbf{x})|_{\partial P_i} = \mathbf{v}_i +
\boldsymbol{\omega}_i\times(\mathbf{x} - \mathbf{a}_i),\\
&\int_{\partial P_i}\boldsymbol{\sigma}\cdot {\bf n} dS=-{\bf F}_i, \quad
\int_{\partial P_i}(\mathbf{x}-\mathbf{a}_i)\times (\boldsymbol{\sigma} \cdot \mathbf{n}) dS=-{\bf T}_i.
\end{aligned}
\end{equation}
Here $\mu$ is the fluid viscosity and the first two equations state
that the fluid motion is a
divergence-free Stokes flow; the third equation specifies the fluid
velocity at infinity;
the fourth equation enforces a rigid body motion constraint on each
particle, where
$\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
angular velocities
of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of $P_i$;
the last two equations state that the net forces and torques
on each particle are given by the quantities ${\bf F}_i$ and ${\bf T}_i$
from \eqref{forceandtorque}, and $\boldsymbol{\sigma}$ is the fluid shear stress.

@@

Our simulations used Janus particles to model
lipid amphiphiles. Janus particles are a popular tool in material science and physics
for creating functional materials \cite{Lee2014, Lee2013}. 
This topic is the basis of Specific Aim 3. Janus particles are typically
spherical with a biphasic material label on either hemisphere,  endowing the particle
with a directional order. We considered a two-dimensional system, and represented an 
elongated lipid by elliptical particles with hydrophobic and hydrophilic labels along the ellipse's long axis.

>>>>

From a phenomenological perspective, (\ref{HAP}--\ref{SL}) 
is an appropriate model of hydrophobic attraction. Specifically,
using boundary layer analysis, it is possible 
to show that $\Phi$ converges to a surface energy in the zero-decay length limit \cite{Lee2018,Lin2015,Shibata2004}.
For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g.~between hydrophobic parallel disks
separated by water \cite{Eriksson1989}. Also, we have demonstrated with simulation that the forces 
derived from HAP theory are non-additive, and even deviate significantly from 
a pairwise potential \cite{Meyer2006,Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

@@

The main analytical tool of our manuscript 
is a formula for the first variation of $\Phi$ \cite{Bandle2015,Schiffer1954,Grinfeld2010}. 
This first variation  is a symmetric, rank-two tensor called the hydrophobic stress:
\begin{equation}
  \label{stress}
\boldsymbol{\sigma}_{\text{hydro}} = \gamma \rho^{-1} u^2 I + 2\rho \gamma (\tfrac{1}{2}|\nabla u|^2I - \nabla u \nabla u^T).
\end{equation}
To obtain \eqref{stress}, we observe that the potential $\Phi$ is a function of the particle position and orientations.
This is because the particle configuration defines the shape of $\Omega$ and the boundary data $f.$ 
Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
in a critical way leads to the surface term \eqref{stress}.  
By integrating the hydrophobic stress over the surface of particle $P_i,$ we obtaining the hydrophobic force and torque on each particle 
\begin{equation}
  \label{forceandtorque}
  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n} \,dS,\quad
  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times (\boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n}) \,dS.
\end{equation}
We verified that this system is force and torque free.
To supply viscous dissipation, 
we incorporated the mobility problem in Stokes flow to obtain the rigid body motions; 
\begin{equation}
\label{eq:stokes}
\begin{aligned}
&-\mu \Delta {\bf u} + \nabla p = 0, \quad \text{in}\ \Omega, \qquad 
\nabla \cdot {\bf u} = 0,  \quad \text{in}\ \Omega,\\
&{\bf u}({\bf x}) \to 0 \quad \text{as}\ |{\bf x}|\to \infty,\qquad 
  \mathbf{u}(\mathbf{x})|_{\partial P_i} = \mathbf{v}_i +
\boldsymbol{\omega}_i\times(\mathbf{x} - \mathbf{a}_i),\\
&\int_{\partial P_i}\boldsymbol{\sigma}\cdot {\bf n} dS=-{\bf F}_i, \quad
\int_{\partial P_i}(\mathbf{x}-\mathbf{a}_i)\times (\boldsymbol{\sigma} \cdot \mathbf{n}) dS=-{\bf T}_i.
\end{aligned}
\end{equation}
Here $\mu$ is the fluid viscosity and the first two equations state
that the fluid motion is a
divergence-free Stokes flow; the third equation specifies the fluid
velocity at infinity;
the fourth equation enforces a rigid body motion constraint on each
particle, where
$\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
angular velocities
of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of $P_i$;
the last two equations state that the net forces and torques
on each particle are given by the quantities ${\bf F}_i$ and ${\bf T}_i$
from \eqref{forceandtorque}, and $\boldsymbol{\sigma}$ is the fluid shear stress.

@@

Our simulations used Janus particles to model
lipid amphiphiles. Janus particles are a popular tool in material science and physics
for creating functional materials \cite{Lee2014, Lee2013}. 
This topic is the basis of Specific Aim 3 \todo[inline]{not true
anymore}. Janus particles are typically
spherical with a biphasic material label on either hemisphere,  endowing the particle
with a directional order. We considered a two-dimensional system, and represented an 
elongated lipid by elliptical particles with hydrophobic and hydrophilic labels along the ellipse's long axis.

### 2020-11-08 NSF2020/Description/broaderimpacts.tex
working on broader impacts section to include Quaife

The proposed mathematical analysis and modeling will provide a transformative
understanding of the collective dynamics of amphiphilic particles such as 
(1) their self-assembly into micelles and bilayers, and 
(2) the interaction between these building blocks.
Amphiphilic Janus particles have gained increasing popularity for fabrication of smart materials.
The proposed hybrid continuum model, mathematical analysis and numerical algorithms will have transformative impact on
precision design for specific mechanical properties of materials made of amphiphilic nanoparticles.
An important component of this proposal is the interdisciplinary education and training of
both undergraduate and graduate students.  The combination of mathematical modeling, analysis and
scientific computing  in this project provides a compelling
example of the importance of mathematics in biophysics and engineering applications.
The concepts and
methods described here go beyond the context of amphiphilic particles and lipid molecules. They extend
to other problems featuring microscopic phase separation that leads to  formation of mesoscopic domains.
This situation arises, for example, in biological development in systems biology.
The methods developed here have the potential to impact those and other related areas in biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The proposed research will have immediate impact on 
undergraduate and graduate education. At the undergraduate level,
the project will involve and support undergraduate researcher from Fordham University.
The supported summer researchers will gain valuable first-hand 
experience in inherently interdisciplinary, mathematical fluid modeling and computation.
We will incorporate research into teaching, especially in differential equation  
and programming courses.

@@

The PIs will capitalize on the synergy between NJIT's doctoral program in Mathematical Sciences 
and Fordham's undergraduate focus in the Department of Mathematics. 
Promising, young undergraduate scientists from the Bronx community 
while find a natural pipeline into graduate studies through working directly 
or indirectly on this project. 
On the graduate-level education, PI Young and co-PI Jiang expect to train and support
a PhD student, Yuexin Liu (who is in her third-year at NJIT) for two more years. Yuexin Liu has past experiences
in the undergraduate training program at NJIT, and will train an undergraduate intern. 
The PIs will foster vertical integration between the senior personnel, their collaborators, postdocs, 
doctoral and Bachelor students, enhancing the
learning environment.
%

@@

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will
reside with the lead PI (Ryham) for this endeavor.  The research work is
structured to meet the tasks discussed in
Sec.~\ref{sec:proposed-work}.
%
The PIs, their postdoc and students will meet frequently in person.
The PIs will share software packages, paper sources, and references on a common
\textsf{Git} repository. The resulting software packages will be posted
on the \textsf{Github} software repository.

>>>>

The proposed mathematical analysis and modeling will provide a
transformative understanding of the collective dynamics of amphiphilic
particles such as (1) their self-assembly into micelles and bilayers,
and (2) the interaction between these building blocks. Amphiphilic Janus
particles have gained increasing popularity for fabrication of smart
materials. The proposed hybrid continuum model, mathematical analysis
and numerical algorithms will have transformative impact on precision
design for specific mechanical properties of materials made of
amphiphilic nanoparticles. An important component of this proposal is
the interdisciplinary education and training of both undergraduate
students, graduate students, and postdoctoral fellows. The combination
of mathematical modeling, analysis, and scientific computing in this
project provides a compelling example of the importance of mathematics
in biophysics and engineering applications. The concepts and methods
described here go beyond the context of amphiphilic particles and lipid
molecules. They extend to other problems featuring microscopic phase
separation that leads to formation of mesoscopic domains. This situation
arises, for example, in biological development in systems biology. The
methods developed here have the potential to impact those and other
related areas in biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The proposed research will have immediate impact on undergraduate and
graduate education. At the undergraduate level, the project will involve
and support undergraduate researcher from Fordham University. The
supported summer researchers will gain valuable first-hand experience in
inherently interdisciplinary, mathematical fluid modeling and
computation. We will incorporate research into teaching, especially in
differential equation and programming courses. PI Quaife will expose
undergraduate and high school students to the reserach through the
Undergraduate Research Opportunity Program (UROP) and Young Scholar's
Program (YSP).

@@

The PIs will capitalize on the synergy between NJIT's doctoral program
in Mathematical Sciences and Fordham's undergraduate focus in the
Department of Mathematics. Promising, young undergraduate scientists
from the Bronx community while find a natural pipeline into graduate
studies through working directly or indirectly on this project. On the
graduate-level education, PI Young and expects to train and
support a PhD student, Yuexin Liu (who is in her third-year at NJIT) for
two more years. Yuexin Liu has past experiences in the undergraduate
training program at NJIT, and will train an undergraduate intern. The
PIs will foster vertical integration between the senior personnel, their
collaborators, postdocs, doctoral and Bachelor students, enhancing the
learning environment.
%

@@

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (Ryham) for this endeavor. The research work is
structured to meet the tasks discussed in
Section~\ref{sec:proposed-work}.
%
The PIs, their postdoc and students will meet frequently in person.  The
PIs will share software packages, paper sources, and references on a
common \textsf{Git} repository. The resulting software packages will be
posted on the \textsf{Github} software repository.

### 2020-11-08 NSF2020/Description/preliminarywork.tex
working on broader impacts section to include Quaife

\begin{figure}[!]
\begin{center}
\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
\end{center}\vspace{-0.3in}
\caption{ 
(A) A vesicle formed by amphiphilic particles in shear flow,
and the tank-treading motion (B)--(D). The separation of particle
pairs in (B) and (C) illustrate inter-leaflet slip.
(E) -- (G) Tank-treading reaches a steady state in elliptical aspect ratio,
major-axis angle, and circumference. }
\label{fig:tanktreading}
\end{figure}
\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 
%The motion of vesicles in shear flow is an important
%problem in the applied mathematics because simulations can reveal mechanical
%properties of membranes and lead to an enhanced understanding of 
%deformable particle laden flows \cite{Sinha15}. 
%
Over the past decades, researchers have used a number of mathematical tools 
to model vesicles in shear flow, including  phase field \cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, 
level set \cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral \cite{Shravan09,Rahimian15} and 
immersed boundary approaches \cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. All these approaches
assume a mathematical surface, whether implicitly or explicitly, 
and define an elastic bending energy of the surface. The vesicle obeys fluid
transport and in turn the fluid balances shear stress with the vesicle's bending force.

@@

\begin{wrapfigure}[17]{l}{0.4\textwidth}
\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
\caption{\label{fig:demixing} An initial assembly of small and 
large particles spontaneous segregates into two smaller bodies. }
\end{wrapfigure}
The HAP simulations show vesicle tank-treading. Under the external shear flow, the initially circular 
vesicle rotates in the clockwise direction. As the rate of rotation increases, the vesicle approaches
a steadily tank-treading ellipse. In Figure \ref{fig:tanktreading}B-D, the solid curves are ellipses fit to the particle centers
and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
and the vesicle diameter is about 14. 
Figure \ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
red and blue curves, yet oscillating in the high-shear rate (yellow) curve.
The tank-treading vesicle elongates and becomes more horizontal 
with an increase in flow rate or 
with a decrease in stiffness (effected by decreasing $\rho = 4$ to $\rho = 2$).

>>>>

\begin{figure}[!]
\begin{center}
\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
\end{center}\vspace{-0.3in}
\caption{(A) A vesicle formed by amphiphilic particles in shear flow,
  and the tank-treading motion (B)--(D). The separation of particle
  pairs in (B) and (C) illustrate inter-leaflet slip.  (E)--(G)
  Tank-treading reaches a steady state in elliptical aspect ratio,
  major-axis angle, and circumference.}
\label{fig:tanktreading}
\end{figure}
\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 
%The motion of vesicles in shear flow is an important
%problem in the applied mathematics because simulations can reveal mechanical
%properties of membranes and lead to an enhanced understanding of 
%deformable particle laden flows \cite{Sinha15}. 
%
Over the past decades, researchers have used a number of mathematical tools 
to model vesicles in shear flow, including  phase field \cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, 
level set \cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral \cite{Shravan09,Rahimian15} and 
immersed boundary approaches \cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. All these approaches
assume a mathematical surface, whether implicitly or explicitly, 
and define an elastic bending energy of the surface. The vesicle obeys fluid
transport and in turn the fluid balances shear stress with the vesicle's bending force.

@@

\begin{wrapfigure}[17]{l}{0.4\textwidth}
\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
\caption{\label{fig:demixing} An initial assembly of small and 
large particles spontaneous segregates into two smaller bodies. }
\end{wrapfigure}
The HAP simulations show vesicle tank-treading. Under the external shear flow, the initially circular 
vesicle rotates in the clockwise direction. As the rate of rotation increases, the vesicle approaches
a steadily tank-treading ellipse. In Figure \ref{fig:tanktreading}B-D, the solid curves are ellipses fit to the particle centers
and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
and the vesicle diameter is about 14. \todo[inline]{missing units. nm?}
Figure~\ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
red and blue curves, yet oscillating in the high-shear rate (yellow) curve.
The tank-treading vesicle elongates and becomes more horizontal 
with an increase in flow rate or 
with a decrease in stiffness (effected by decreasing $\rho = 4$ to $\rho = 2$).

### 2020-11-08 NSF2020/Description/specificaim1_ver2.tex
working on broader impacts section to include Quaife

\section{Proposed Research}
\label{sec:proposed-work}
The proposed research develops fast,
high-order-accurate, parallel numerical algorithms for large-scale
simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
%
We have demonstrated that our hydrophobic attraction with repulsion potential (HARP) approach efficiently simulates
self-assembly of amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu2018_SIAM}, and
recreates the tank-treading phenomenon in external shear flows \cite{Fu20} \textbf{!!let's put a proceedings here so we have something to cite!!}.
%
While the results show great promise in the field of collective body hydrodynamics,
several outstanding issues need to be addressed. These include a thorough 
analysis of elastic properties of our coarse-grained bilayers, and 
efficiently simulating three-dimensional collective hydrodynamics of amphiphilic particles.
Finally, we must mathematically characterize the variational behavior of HARP under appropriate homogenized limits.

@@

An interesting and challenging feature of \eqref{ansatz3} is that
the elastic energy couples director gradients to surface geometry through the tilt vector field.
In biological contexts, bilayer energy is the sum monolayer energies, and tilt appears at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.  
Under spatial scales much larger than the membrane thickness, membrane energy is well-characterized by
the Canham-Helfrich energy used throughout the fluid-structure literature 
\cite{QiangDu09, Lowengrub07,KimLai2010_JCP,Hu,HuLaiSeolEtAl2016_JCP} \textbf{!! YNY and BQ, place your recent works here!!}.
The Canham-Helfrich energy is actually a special case of \eqref{ansatz3} obtained by setting $n =  \pm N$ (the $\pm$ depending
on orientation) and collapsing both monolayers onto the membrane midplane. There,
splay $\Div n$ equal to twice the mean curvature, saddle splay $\det \nabla n$ equal to the Gauss curvature,
and both twist and tilt are equal to zero.

@@

% Proposers should address what they want to do,
% why they want to do it,
% how they plan to do it,
% how they will know if they succeed,
% and what benefits could accrue if the project is successful.
\begin{center}
Preliminary results
\end{center}
Our preliminary tested for elastic properties by subjecting bilayers to external loads \cite{Fu2018_SIAM}.
We used realistic values for the phospholipid length $a$ \cite{Boal},
screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
model parameters.
The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
particle diameter and the hydrophobic boundary condition \eqref{SL}
are additional parameters defining the coarse-grained representation.

@@

\begin{center}
Anticipated model simulations
\end{center}
To characterize material properties, we compare the energies and forces generated by
a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
The comparison enables us to understand how the model parameters map onto elastic parameters.

>>>>

\section{Proposed Research}
\label{sec:proposed-work}
The proposed research develops fast,
high-order-accurate, parallel numerical algorithms for large-scale
simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
%
We have demonstrated that our hydrophobic attraction with repulsion potential (HARP) approach efficiently simulates
self-assembly of amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu2018_SIAM}, and
recreates the tank-treading phenomenon in external shear flows
\cite{Fu20} \todo[inline]{!!let's put a proceedings here so we have something to cite!!}.
%
While the results show great promise in the field of collective body hydrodynamics,
several outstanding issues need to be addressed. These include a thorough 
analysis of elastic properties of our coarse-grained bilayers, and 
efficiently simulating three-dimensional collective hydrodynamics of amphiphilic particles.
Finally, we must mathematically characterize the variational behavior of HARP under appropriate homogenized limits.

@@

An interesting and challenging feature of \eqref{ansatz3} is that the
elastic energy couples director gradients to surface geometry through
the tilt vector field.  In biological contexts, bilayer energy is the
sum monolayer energies, and tilt appears at lipid domain boundaries, the
edge of nanopores and at the boundary of membrane inclusions
\cite{PhysRevE.102.042406}.  Under spatial scales much larger than the
membrane thickness, membrane energy is well-characterized by the
Canham-Helfrich energy used throughout the fluid-structure literature
\cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP,
qua-bir2014, qua-vee-you2019}. \todo[inline]{YNY: place your recent
works here} The Canham-Helfrich energy is actually a special case of
\eqref{ansatz3} obtained by setting $n =  \pm N$ (the $\pm$ depending on
orientation) and collapsing both monolayers onto the membrane midplane.
There, splay $\Div n$ equal to twice the mean curvature, saddle splay
$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
are equal to zero.

@@

% Proposers should address what they want to do,
% why they want to do it,
% how they plan to do it,
% how they will know if they succeed,
% and what benefits could accrue if the project is successful.
%\begin{center}
%Preliminary results
%\end{center}
\subsubsection{Preliminary results}
Our preliminary tested for elastic properties by subjecting bilayers to external loads \cite{Fu2018_SIAM}.
We used realistic values for the phospholipid length $a$ \cite{Boal},
screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
model parameters.
The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
particle diameter and the hydrophobic boundary condition \eqref{SL}
are additional parameters defining the coarse-grained representation.

@@

%\begin{center}
%Anticipated model simulations
%\end{center}
\subsubsection{Anticipated model simulations}
To characterize material properties, we compare the energies and forces generated by
a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
The comparison enables us to understand how the model parameters map onto elastic parameters.
